### 2013-08-14 exact_learning/paper.tex
somewhat better structure in pystruct part, misc

\section{Discussion}
In this work we demonstrated that it is possible to learn state-of-the-art CRF models
exactly using structural support vector machines, despite the model containing many loops.
The key to efficient learning is the combination of different inference mechanisms and
a novel caching scheme for the one-slack cutting plane method, in combination
with state-of-the-art inference methods.

>>>>

\section{Summary}
In this chapter we demonstrated that it is possible to learn state-of-the-art CRF models
exactly using structural support vector machines, despite the model containing many loops.
The key to efficient learning is the combination of different inference mechanisms and
a novel caching scheme for the one-slack cutting plane method, in combination
with state-of-the-art inference methods.

### 2013-08-14 pystruct/paper.tex
somewhat better structure in pystruct part, misc

%The organization of this paper is as follows. Section~\ref{sec:api} revisits
%the basic concepts of structured learning algorithms, and how these map to the
%\pystruct interface. Section~\ref{sec:examples} exemplifies the use of \pystruct
%on some standard structured prediction benchmarks and showcasts how \pystruct
%can interact with existing libraries, foremost scikit-learn and scikit-image.
%Section~\ref{sec:benchmarks} finally compares \pystruct with SVM$^\text{struct}$,
%arguably the most widely used implementation of structural SVMs, and
%SVM$^\text{python}$, a Python interface or the same.

@@

\section{Project Goals}\label{sec:goals}

@@

\section{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%TODO Multi-label, chain?

@@

\section{Experiments}\label{sec:benchmarks}
While \pystruct focuses on usability and covers a wide range of applications, it is also
important that the implemented learning algorithms run in acceptable time.
In this section, we compare our implementation of the one-slack cutting plance
algorithm with the implementation in \svmstruct.
We compare performance of the Crammer-Singer multi-class SVM with respect to
learning time and accuracy on the MNIST dataset of handwritten digits.
While multi-class classification is not very interesting from a structured
prediction point of view, this problem is well-suited to benchmark the cutting
plane solvers with respect to accuracy and speed.

@@

\section{Summary}
%TODO summarize structured prediction
This paper introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.

>>>>

%The organization of this chapter is as follows. Section~\ref{sec:api} revisits
%the basic concepts of structured learning algorithms, and how these map to the
%\pystruct interface. Section~\ref{sec:examples} exemplifies the use of \pystruct
%on some standard structured prediction benchmarks and showcasts how \pystruct
%can interact with existing libraries, foremost scikit-learn and scikit-image.
%Section~\ref{sec:benchmarks} finally compares \pystruct with SVM$^\text{struct}$,
%arguably the most widely used implementation of structural SVMs, and
%SVM$^\text{python}$, a Python interface or the same.

@@

\subsection{Project Goals}\label{sec:goals}

@@

\subsection{Usage Example: Semantic Image Segmentation}\label{sec:examples}
%TODO Multi-label, chain?

@@

\subsection{Experiments}\label{sec:benchmarks}
While \pystruct focuses on usability and covers a wide range of applications, it is also
important that the implemented learning algorithms run in acceptable time.
In this section, we compare our implementation of the one-slack cutting plance
algorithm with the implementation in \svmstruct.
We compare performance of the Crammer-Singer multi-class SVM with respect to
learning time and accuracy on the MNIST dataset of handwritten digits.
While multi-class classification is not very interesting from a structured
prediction point of view, this problem is well-suited to benchmark the cutting
plane solvers with respect to accuracy and speed.

@@

\section{Summary}
%TODO summarize structured prediction
This chapter introduced \pystruct, a modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations.
\pystruct integrates itself into the scientific Python eco-system, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches. In the future,
we plan to integrate other paradigms, such as sampling-based learning~\citep{wick2011samplerank},
surrogate objectives (for example pseudo-likelihood), and approaches that allow for a better integration
of inference and learning~\citep{meshi2010learning}.
